---
title: "Results-Main"
author: "Neomi Rao"
date: '2022-06-01'
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(lubridate)
library(jsonlite)
library(knitr)
library(kableExtra)
library(ggrepel)
library(stm)
library(academictwitteR)
library(broom)

load(file="data/defundtweets1320_nolist_df.Rda")
load(file="data/defund_may2020_stm_15k.Rda")
load(file="data/mergeduser_defund_df.Rda") 
load(file = "data/prep_may20_plots.Rda")
```

## Methods
Total number of tweets, unique users in big dataset (through June 2020)
```{r}
#total number of tweets in big dataset
nrow(defund1320_nolist)

#number of unique users in big dataset
length(unique(defund1320_nolist$author_id))
```


Small dataset: total number of tweets, unique users, and engagement levels by time period (2013-14, 2015-16, 2017-May 2020)
Note - I'm using mean engagement rather than median or max because it seems most useful (also max doesn't map onto qualitative data after removing duplicate tweets)
*NOTE : MAKE THIS PRETTY AND AUTOMATICALLY INTO A TABLE*
```{r}
defund13may20 <- defund1320_nolist %>%
  filter(str_detect(text, "(?i)defund", )) %>%
  filter(date <= as.Date("2020-05-25")) %>%
  #filter(!str_detect(text, "^RT")) %>%
  #distinct(conversation_id, .keep_all = T) %>%
  mutate(engagement = public_metrics.retweet_count + public_metrics.reply_count + 
                          public_metrics.like_count + public_metrics.quote_count)


#2013-2014
defund1314 <- defund13may20 %>% 
    filter(date <= as.Date("2014-12-31")) 
nrow(defund1314) #number of tweets
length(unique(defund1314$author_id)) #number of unique users
mean(defund1314$engagement) #mean engagement
#max(defund1314$engagement) #max engagement
#sd(defund1314$engagement)

#2015-2016
defund1516 <- defund13may20 %>% 
    filter(date > as.Date("2014-12-31") & date <= as.Date("2016-12-31")) 
nrow(defund1516) #number of tweets
length(unique(defund1516$author_id)) #number of unique users
mean(defund1516$engagement) #mean engagement
#max(defund1516$engagement) #max engagement

#2017-May2020
defund17may20 <- defund13may20 %>% 
    filter(date > as.Date("2016-12-31")) 
nrow(defund17may20) #number of tweets
length(unique(defund17may20$author_id)) #number of unique users
mean(defund17may20$engagement) #mean engagement
#max(defund17may20$engagement) #max engagement

  #May2020-June2020
  defundmayjun20 <- defund1320_nolist %>% 
      filter(date > as.Date("2020-05-25") & date <= as.Date("2020-06-04")) %>%
      mutate(engagement = public_metrics.retweet_count + public_metrics.reply_count + 
                          public_metrics.like_count + public_metrics.quote_count)
  nrow(defundmayjun20) #number of tweets
  length(unique(defundmayjun20$author_id)) #number of unique users
  mean(defundmayjun20$engagement) #mean engagement
  #max(defund17may20$engagement) #max engagement

```



**Figure 1:** Frequency of tweets that contain both "defund" and "police" (or cognates) from January 2013 through June 2020
```{r early_freq, echo=F}
defundfreq_1320 <- defund1320_nolist %>%
  filter(str_detect(text, "(?i)defund", )) %>%
  ggplot(aes(x=date)) +   
  stat_count(geom='line', aes(y=..count..)) +
  labs(title = "A) Daily frequency of 'defund police' tweets\n(1/2013-6/2020)") +
  xlab("Date") + ylab("Daily count of tweets") +
  annotate(geom = "vline",
             x = c(ymd("2020-05-25")),
             xintercept = c(ymd("2020-05-25")),
             linetype = c("dashed"),  colour = "red") +
  annotate(geom = "text",
             label = c("May 25, 2020"),
             x = c(ymd("2020-05-05")), y = c(50000),
             angle = 90, vjust = 0, hjust=0.5, colour = "red", size=5) +
  theme_bw()+ 
  theme(axis.text = element_text(size=16), axis.title = element_text(size=16), 
           plot.title=element_text(size=20))

ggsave(filename = "figures/defundfreq_2013-20.png", plot = defundfreq_1320)

#which dates have the most tweets?
#defund1320_nolist %>% count(date, sort = T) %>% slice_head(., n=10)

# version with logged y axis
defundfreq_1320_log <- defund1320_nolist %>%
  filter(str_detect(text, "(?i)defund", )) %>%
  group_by(date) %>%
  summarise(frequency1=(n()+1)) 

defundfreq_1320_log <-
  ggplot(data=defundfreq_1320_log, aes(x=date, y=frequency1)) +  
  geom_line() +
  scale_y_log10() + #log scale y axis
  labs(title = "Logged daily frequency of 'defund police' tweets\n(1/2013-6/2020)") +
  xlab("Date") + ylab("Logged daily count of tweets") +
  annotate(geom = "vline",
             x = c(ymd("2020-05-25")),
             xintercept = c(ymd("2020-05-25")),
             linetype = c("dashed"),  colour = "red") +
  annotate(geom = "text",
             label = c("May 25, 2020"),
             x = c(ymd("2020-05-05")), y = c(1000),
             angle = 90, vjust = 0, hjust=0.5, colour = "red", size=5) +
  theme_bw()+ 
  theme(axis.text = element_text(size=16), axis.title = element_text(size=16), 
           plot.title=element_text(size=20))
  
ggsave(filename = "figures/defundfreq_2013-20_log.png", plot = defundfreq_1320_log)

```

**Figure 2:** Frequency of tweets that contain both "defund" and "police" (or cognates) from January 2013 through May 2020
```{r early_freq2, echo=F warning=F}
defundfreq_13may20 <- defund1320_nolist %>%
  filter(str_detect(text, "(?i)defund", )) %>%
  filter(date <= as.Date("2020-05-25")) %>%
  ggplot(aes(x=date)) +   
  stat_count(geom='line', aes(y=..count..)) +
  labs(title = "B) Daily frequency of 'defund police' tweets\n(1/1/2013-5/25/2020)") +
  xlab("Date") + ylab("Daily count of tweets") +
  annotate(geom = "vline",
             x = c(ymd("2020-05-25")),
             xintercept = c(ymd("2020-05-25")),
             linetype = c("dashed"),  colour = "red") +
  annotate(geom = "text",
             label = c("May 25, 2020"),
             x = c(ymd("2020-05-25")), y = c(1000),
             angle = 90, vjust = 0, hjust=0.5, colour = "red", size=5) +
  theme_bw()+
  theme(axis.text = element_text(size=16), axis.title = element_text(size=16), 
           plot.title=element_text(size=20))

defundfreq_13may20

ggsave(filename = "figures/defundfreq_2013-may20.png", plot = defundfreq_13may20)

```


## Results
What is the expected proportion of each topic for defund Tweets prior to May 25, 2020? (FREX)
```{r}
# Corpus summary
png(filename="figures/defund15_topicprop.png", width = 600, height = 500)
plot.STM(defund_model_15, type="summary", 
         #topics = c(1, 3, 5:15), 
         n=5, labeltype = "frex",
         main="Expected Proportions for 'Defund Police' Tweets \n(Top FREX Words for 15 Topics)")
dev.off()

```

Graph of all 12 topics (excluding 2 & 4 & 15)
```{r}
#see excel file stmplot-xaxis-dates.xlsx for 
png(filename="figures/defundtopics_all.png", width = 800, height = 800)
#remove box around plot, make line weight thicker
par(bty="n",lwd=2) 
#plot!
plot(prep_may20, "month", method = "continuous", topics = c(1, 3, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14), 
     model = defund_model_15, 
     printlegend = F, xaxt="n", xlab = "Time (Jan 2013-May 2020)",
     main = "'Defund Police' Tweets: Topic Proportions Over Time", 
     cex.lab = 1.5, cex.axis = 1.2, cex.main = 2) #increase font sizes
#custom axis
axis(1, at = c(15706, 16071, 16436, 16801, 17167, 17532, 17897, 18262), 
     labels = c("2013", "2014", "2015", "2016", "2017", "2018", "2019", "2020"),
     cex.axis = 1.5)
# Put dotted lines on the x axis at each election year.
abline(v=c(15706, 16071, 16436, 16801, 17167, 17532, 17897, 18262),lty=2,lwd=1,col="grey45") 
#custom legend
legend("bottom",
       legend=c("[1] Direct Actions to Defund/ Dismantle", "[3] Clinton Conspiracy + Blue Lives", 
                "[5] Demand POTUS Demil/ Disarm/ Reform", "[6] Tell Obama: Hit Police Pockets", 
                "[7] BYP100-FundBlackFutures", "[8] DOJ: Defund/ Disarm/ Abolish", 
                "[9] No Federal $ for Militarization", "[10] Bitcoin Defunds Police State",
                "[11] Right-wing Conspiracy", "[12] Anti-BLM/BYP", "[13] Police Violence Incidents", 
                "[14] Reimagine Public Safety"), 
      col=c("red", "orange", "#FFED3A", "#b9fb60", "#51FA3A", "#45FA6D", 
            "#47FCCD", "#027FFF", "#2633FF", "#AF5EFF", "#FF54EE", "#FF639C"), 
      lty=1.5, box.lty = 0, cex = 1.3, ncol=2)
dev.off()
```

Select topics to graph for comparison
```{r}
png(filename="figures/defundtopics_ofinterest2.png", width = 800, height = 800)
#remove box around plot, make line weight thicker
par(bty="n",lwd=2) 
plot(prep_may20, "month", method = "continuous", topics = c(1, 6, 7, 10, 11, 12, 14), 
     model = defund_model_15, 
     printlegend = F, xaxt="n", xlab = "Time (Jan 2013-May 2020)",
     main = "'Defund Police' Tweets: Selected Topic Proportions Over Time", 
     cex.lab = 1.5, cex.axis = 1.2, cex.main = 2) #increase font sizes
#dotted lines for years
abline(v=c(15706, 16071, 16436, 16801, 17167, 17532, 17897, 18262),lty=2,lwd=1,col="grey45")
#custom axis
axis(1, at = c(15706, 16071, 16436, 16801, 17167, 17532, 17897, 18262), 
     labels = c("2013", "2014", "2015", "2016", "2017", "2018", "2019", "2020"),
     cex.axis = 1.5)
#custom legend
legend("bottomright",
       legend=c("[1] Direct Actions to Defund/ Dismantle",
                "[6] Tell Obama: Hit Police Pockets", "[7] BYP100-FundBlackFutures", 
                "[10] Bitcoin Defunds Police State", "[11] Right-wing Conspiracy",
                "[12] Anti-BLM/BYP", "[14] Reimagine Public Safety"), 
      col=c("red", "#FFDB00", "green", "aquamarine", "#279DFF", "blue", "magenta"), 
      lty=1.5, box.lty = 0, cex = 1.4)
dev.off()
```



### 2013-2014
Graph of selected topics for 2013-2014
```{r}
png(filename="figures/defundtopics_2013-14.png", width = 800, height = 800)
#remove box around plot, make line weight thicker
par(bty="n",lwd=2) 

#plot!
plot(prep_may20, "month", method = "continuous", topics = c(1, 6, 7, 10, 11, 12, 14), 
     model = defund_model_15, 
     printlegend = F, xaxt="n", xlab = "Time (Jan 2013-Dec 2014)",
     xlim = c(15706, 16435),
     main = "'Defund Police' Tweets: Select Topic Proportions 2013-2014", 
     cex.lab = 1.5, cex.axis = 1.2, cex.main = 2) #increase font sizes
#custom axis
axis(1, at = c(15706, 15887, 16071, 16252, 16405), #each +1 is +1 day
     labels = c("Jan 2013", "July 2013", "Jan 2014", "July 2014", "Dec 2014"),
     cex.axis = 1.5)
# Put dotted lines on the x axis at each election year.
abline(v=c(15706, 15887, 16071, 16252, 16405),lty=2,lwd=1,col="grey45") 
#custom legend
legend("bottomright",
       legend=c("[1] Direct Actions to Defund/ Dismantle",
                "[6] Tell Obama: Hit Police Pockets", "[7] BYP100-FundBlackFutures", 
                "[10] Bitcoin Defunds Police State", "[11] Right-wing Conspiracy",
                "[12] Anti-BLM/BYP", "[14] Reimagine Public Safety"), 
      col=c("red", "#FFDB00", "green", "aquamarine", "#279DFF", "blue", "magenta"), 
      lty=1.5, box.lty = 0, cex = 1.4)

dev.off()
```

Table of highest engagement tweets in dataset:
Time period 1: Jan 2013-Dec 2014
```{r}
#top 15 max engagement defund tweets from 1/13-12/14
#use defund merge dataset (user data)
t1_top20 <- defund_merge %>%
  filter(str_detect(text, "(?i)defund", )) %>%
  filter(!str_detect(text, "^RT")) %>%
  filter(date <= as.Date("2014-12-31")) %>%
  mutate(engagement = public_metrics.retweet_count + public_metrics.reply_count + 
                          public_metrics.like_count + public_metrics.quote_count) %>%
  distinct(text, .keep_all = T) %>%
  select(date, text, engagement, username, description) %>%
  slice_max(order_by=engagement, n=20)%>%
  arrange(date)

kableExtra::kable_styling(knitr::kable(t1_top20, caption="Most Engaged Tweets about defunding police (2013-2014", escape = FALSE))
write.table(t1_top20, file = "tables/top20_2013-14_table.txt", sep = "╡", quote = FALSE, row.names = F)


#test pre-october 2015
#use defund merge dataset (user data)
test <- defund_merge %>%
  filter(str_detect(text, "(?i)defund", )) %>%
  filter(!str_detect(text, "^RT")) %>%
  filter(date <= as.Date("2015-10-01")) %>%
  mutate(engagement = public_metrics.retweet_count + public_metrics.reply_count + 
                          public_metrics.like_count + public_metrics.quote_count) %>%
  distinct(text, .keep_all = T) %>%
  select(date, text, engagement, username, description) %>%
  slice_max(order_by=engagement, n=40)%>%
  arrange(date)

```




### 2015-2016

Graph of selected 12 topics for 2015-2016
```{r}
png(filename="figures/defundtopics_2015-16.png", width = 800, height = 800)
#remove box around plot, make line weight thicker
par(bty="n",lwd=2) 

#plot!
plot(prep_may20, "month", method = "continuous", topics = c(1, 6, 7, 10, 11, 12, 14), 
     model = defund_model_15, 
     printlegend = F, xaxt="n", xlab = "Time (Jan 2015-Dec 2016)",
     xlim = c(16436, 17166),
     main = "'Defund Police' Tweets: Select Topic Proportions 2015-2016", 
     cex.lab = 1.5, cex.axis = 1.2, cex.main = 2) #increase font sizes
#custom axis
axis(1, at = c(16436, 16671, 16801, 16983, 17136), # Jan# + 181 = Jul#
     labels = c("Jan 2015", "July 2015", "Jan 2016", "July 2016", "Dec 2016"),
     cex.axis = 1.5)
# Put dotted lines on the x axis at each election year.
abline(v=c(16436, 16671, 16801, 16982, 17136),lty=2,lwd=1,col="grey45") 
#custom legend
legend("bottomright",
       legend=c("[1] Direct Actions to Defund/ Dismantle",
                "[6] Tell Obama: Hit Police Pockets", "[7] BYP100-FundBlackFutures", 
                "[10] Bitcoin Defunds Police State", "[11] Right-wing Conspiracy",
                "[12] Anti-BLM/BYP", "[14] Reimagine Public Safety"), 
      col=c("red", "#FFDB00", "green", "aquamarine", "#279DFF", "blue", "magenta"), 
      lty=1.5, box.lty = 0, cex = 1.4)

dev.off()
```

Time period 2: Oct 2015-Oct 2016
```{r}
#top 20 max engagement defund tweets from 10/15-10/16
#use defund merge dataset (user data)
t2_top20 <- defund_merge %>%
  filter(str_detect(text, "(?i)defund", )) %>%
  filter(!str_detect(text, "^RT")) %>%
  filter(date >= as.Date("2015-01-01") & date <= as.Date("2016-12-31")) %>%
  mutate(engagement = public_metrics.retweet_count + public_metrics.reply_count + 
                          public_metrics.like_count + public_metrics.quote_count) %>%
  distinct(text, .keep_all = T) %>%
  select(date, text, engagement, username, description) %>%
  slice_max(order_by=engagement, n=20)%>%
  arrange(date)

kableExtra::kable_styling(knitr::kable(t2_top20, caption="Most Engaged Tweets about defunding police (2015-2016", escape = FALSE))
write.table(t2_top20, file = "tables/top20_2015-16_table.txt", sep = "╡", quote = FALSE, row.names = F)


```

### 2017-2020
Graph of selected topics for 2017-2020
```{r}
png(filename="figures/defundtopics_2017-20.png", width = 800, height = 800)
#remove box around plot, make line weight thicker
par(bty="n",lwd=2) 

#plot!
plot(prep_may20, "month", method = "continuous", topics = c(1, 6, 7, 10, 11, 12, 14), 
     model = defund_model_15, 
     printlegend = F, xaxt="n", xlab = "Time (Jan 2017-May 2020)",
     xlim = c(17167,18408),
     main = "'Defund Police' Tweets: Select Topic Proportions 2017-2020", 
     cex.lab = 1.5, cex.axis = 1.2, cex.main = 2) #increase font sizes
#custom axis
axis(1, at = c(17167, 17532, 17897, 18262), # Jan# + 181 = Jul#
     labels = c("Jan 2017", "Jan 2018", "Jan 2019", "Jan 2020"),
     cex.axis = 1.5)
# Put dotted lines on the x axis at each election year.
abline(v=c(17167, 17532, 17897, 18262),lty=2,lwd=1,col="grey45") 
#custom legend
legend("bottomright",
       legend=c("[1] Direct Actions to Defund/ Dismantle",
                "[6] Tell Obama: Hit Police Pockets", "[7] BYP100-FundBlackFutures", 
                "[10] Bitcoin Defunds Police State", "[11] Right-wing Conspiracy",
                "[12] Anti-BLM/BYP", "[14] Reimagine Public Safety"), 
      col=c("red", "#FFDB00", "green", "aquamarine", "#279DFF", "blue", "magenta"), 
      lty=1.5, box.lty = 0, cex = 1.4)

dev.off()
```

Time period 3: Jan 2017-May 2020
```{r}
#top 20 max engagement defund tweets from 1/17-5/25/20
#use defund merge dataset (user data)
t3_top20 <- defund_merge %>%
  filter(str_detect(text, "(?i)defund", )) %>%
  filter(!str_detect(text, "^RT")) %>%
  filter(date >= as.Date("2017-01-01") & date <= as.Date("2020-05-25")) %>%
  mutate(engagement = public_metrics.retweet_count + public_metrics.reply_count + 
                          public_metrics.like_count + public_metrics.quote_count) %>%
  distinct(text, .keep_all = T) %>%
  select(date, text, engagement, username, description) %>%
  slice_max(order_by=engagement, n=20)%>%
  arrange(date)

kableExtra::kable_styling(knitr::kable(t3_top20, caption="Most Engaged Tweets about defunding police (2017-2020", escape = FALSE))
write.table(t3_top20, file = "tables/top20_2017-20_table.txt", sep = "╡", quote = FALSE, row.names = F)

```


Time period 4: May 26 2020-June 4
```{r}
library(academictwitteR)

bearer_token <- "AAAAAAAAAAAAAAAAAAAAAA0IYwEAAAAA59YYFaUNEiGx9iUbhAG%2FY%2FY%2Byp0%3D1Y3siHnHXCseUuKnAheOjifcBPskzwETs1juDCtpPXinTTeZZs"

#top 20 max engagement defund tweets
#merge in user data
t4_top20_a <- defund1320_nolist %>%
  filter(date >= as.Date("2020-05-26") & date <= as.Date("2020-06-04")) %>%
  filter(str_detect(text, "(?i)defund")) %>%
  filter(!str_detect(text, "^RT")) %>%
  mutate(engagement = public_metrics.retweet_count + public_metrics.reply_count + 
                          public_metrics.like_count + public_metrics.quote_count) %>%
  slice_max(., order_by = engagement, n=21)

t4_top20 <- t4_top20_a$author_id %>%
  get_user_profile(., bearer_token) %>% #load this data in so we're not actively pulling from twitter
  merge(., t4_top20_a, by.x = "id", by.y = "author_id", all=F) %>%
  distinct(username, .keep_all = T) %>%
  select(date, text, engagement, username, description) %>%
  arrange(date)


kableExtra::kable_styling(knitr::kable(t4_top20, caption="Most Engaged Tweets about defunding police (May 26, 2020-June 4, 2020)", escape = FALSE))
write.table(t4_top20, file = "tables/top20_mayjune-20_table.txt", sep = "╡", quote = FALSE, row.names = F)

```
